Research Notes

### 2018-03-06 writups/notes.tex
stash

@@

This requires we compute a ton of extra points though. Ideally, we want to use
BCs. Based on our explicit solution \autoref{eq:strat.full_sol} we might expect
to write something like $\pd{u_{1z}}{z} = \frac{1/2H +
ik_z}{\mp i\omega}\pd{u_{1z}}{z} \approx \pm \frac{k_z}{\omega}\pd{u_{1z}}{z}$.
For an outgoing wave we expect to choose the negative sign.

>>>>

\subsection{Waveform Properties, Analytical}

Let's figure out the analytical forms for the phase, group velocity and the
energy density/power flux. We will try to recover these from waveforms.

For our stratified atmosphere problem, $\omega^2 = \frac{N^2 k_x^2}{k^2 +
\frac{1}{4H^2}}$. Plugging in our parameters $k_z = -k_x = 2pi, N^2 = 10$ we can
find $\omega \approx 2.23\;\mathrm{Hz}$, so $\vec{v}_{ph} \approx
0.1777\p*{-\hat{x} + \hat{z}}\;\mathrm{s^{-1}}$.

Since we use a height of $5$, we should expect the initial disturbance to reach
the top boundary at $t \sim 30\;\mathrm{s}$.

On the other hand the group velocity is given $\vec{v}_g =
\pd{\omega}{k_i}\hat{\imath}$. In our problem, $v_{g, z} =
-\frac{N^2k_x^2k_z}{\p*{k_x^2 + k_z^2 + 1/4H^2}^{3/2}}$ while $v_{g, x} =
\frac{2N^2k_x}{\sqrt{k_x^2 + k_z^2 + 1/4H^2}} - \frac{N^2k_x^3}{\p*{k_x^2 +
k_z^2 + 1/4H^2}^{3/2}}$.

We should note that the kinetic energy density is just $E = \frac{1}{2}\rho
v^2$, the kinetic energy. Using then $\rd{E}{t} = 0$ shows that the
corresponding power flux is $\vec{P} = \frac{\vec{v}}{2}\rho v^2$.

@@

This requires we compute a ton of extra points though. Ideally, we want to use
BCs. TODO
